Grounding the interaction: anchoring situated discourse in everyday human-robot interaction

### 2011-07-16 paper_knowledge.tex
Add references to spark

Second, the \emph{illocutionary force}, \ie the \emph{intent} of the utterance
as thought by the agent, must be extracted and understood. In our example,
Thomas obviously wants an action to be performed by the robot. The action
parametrization is conveyed by the semantics attached to the words and the
grammatical structure of the sentence. In our example, the type of action is
given by the verb ``\textit{give}''. Assuming the robot has some procedural
knowledge attached to this symbol, the action type can be considered as
grounded for the robot. We can as well understand that the recipient of the
action is the human, the performer is the robot itself, and the object acted
upon is the tape. These are the basic \emph{thematic roles}~\cite{Gruber1965}
that can be extracted from the sentence that allow for fully grounding the action
\footnote{The third class of speech acts, the \emph{perlocutionary acts}, deals
with implicit speaker's expectations. We will not consider it further in this
article}.

@@

\item \emph{Location according to an agent}: The predicate
\concept{isLocatedAt} represents spatial locations between agents and objects.
For example we say ``it is on my right, on your left, ...'' We compute these
spatial locations by dividing the space around the referent (an agent) into $n$
regions based on arbitrary angle values relative to the referent orientation.
For example, for $n = 4$ we would have the space divided into \emph{front,
left, right} and \emph{back}. Additionally, two proximity values, \emph{near}
and \emph{far}, may also be considered. The number of regions and proximity
values can be chosen depending on the context where the interaction takes
place.

\item \emph{Location according to an object}: We can also refer to object
locations with respect to other objects in the environment, such as \emph{above,
next to, in}, etc. These types of relations are widely studied in language
grounding (\eg \cite{Regier01} presented different models to define the
\emph{above} relation). In this work we use similar models based on the
bounding boxes and center of mass of the objects to define three main relations
(Figure~\ref{fig::sprelation}):

>>>>

Second, the \emph{illocutionary force}, \ie the \emph{intent} of the utterance
as thought by the agent, must be extracted and understood. In our example,
Thomas obviously wants an action to be performed by the robot. The action
parametrization is conveyed by the semantics attached to the words and the
grammatical structure of the sentence. In our example, the type of action is
given by the verb ``\textit{give}''. Assuming the robot has some procedural
knowledge attached to this symbol, the action type can be considered as
grounded for the robot. We can as well understand that the recipient of the
action is the human, the performer is the robot itself, and the object acted
upon is the tape. These are the basic \emph{thematic roles}~\cite{Gruber1965}
that can be extracted from the sentence that allow for fully grounding the action
\footnote{The third class of speech acts, the \emph{perlocutionary acts}, deal
with implicit speaker's expectations. We will not consider it further in this
article}.

@@

\item \emph{Location according to an agent}: The predicate
\concept{isLocatedAt} represents spatial locations between agents and objects.
For example we say ``it is on my right, on your left, ...'' These type of direction commands are studied
in the literature in the context of language grounding (\eg \cite{OKeefe1999,Matuszek10}). We compute these
spatial locations by dividing the space around the referent (an agent) into $n$
regions based on arbitrary angle values relative to the referent orientation.
For example, for $n = 4$ we would have the space divided into \emph{front,
left, right} and \emph{back}. Additionally, two proximity values, \emph{near}
and \emph{far}, may also be considered. The number of regions and proximity
values can be chosen depending on the context where the interaction takes
place.

\item \emph{Location according to an object}: We can also refer to object
locations with respect to other objects in the environment, such as \emph{above,
next to, in}, etc. These types of relations are widely studied in language
grounding (\eg \cite{Regier01} presented different models to define the
\emph{above} relation; \cite{Kelleher09} presented two computational models of topological and projective spatial prepositions; \cite{Blisard05} employed contour points of segmented objects to determine \emph{front, behind, left,right} relations). In this work we use similar models based on the
bounding boxes and center of mass of the objects to define three main relations
(Figure~\ref{fig::sprelation}):
